Predictors of frog survival following translocations - supplemental analyses

### 2022-11-01 code/translocation_survival_analysis_suppl.Rmd
Add description of dataset columns

## Analyze dataset
### Read in data, standardize variables
```{r}
d1 <- read_csv(here::here("data", "clean", "bd_beforeafter_translocation.csv")) %>% 
  mutate(after = if_else(period == "after", 1, 0),
         bd_load = as.integer(round(bd_load)),  # if using negative binomial distribution
         after_c = after - mean(after))
```

>>>>

### Description of dataset columns 
-  site_id: Unique 5-digit site identifier.  
-  site_id1: Assigned 5-digit site identifier for a collection of nearby sites utilized by a frog population.
-  translocation_id: Unique identifier for each translocation.  
-  visit_date: Date on which translocation/survey was conducted.  
-  survey_type: "translocation" or "cmr".  
-  period: "before" or "after" translocation.
-  year_translocate: Year in which translocation was conducted.  
-  year_capture: Year in which frog was captured.  
-  interval: Number of years between translocation and frog capture.  
-  pit_tag_ref: Unique PIT tag identifier.  
-  swab_id: Unique identifier for skin swab sample.  
-  bd_load: Bd infection intensity determined from skin swab sample, units are number of ITS1 copies * 80.

## Analyze dataset
### Read in data, standardize variables
```{r}
d1 <- read_csv(here::here("data", "clean", "bd_beforeafter_translocation.csv")) %>% 
  mutate(after = if_else(period == "after", 1, 0),
         bd_load = as.integer(round(bd_load)), 
         after_c = after - mean(after))
```
